---
echo: false
warning: false
---

```{r}
library(surveydown)
library(shiny)
library(DT)
```

::: {#welcome .sd-page}
# Welcome to our survey!

Some text about the workflow here...

```{r q-indOrRec}
sd_question(
  type  = 'mc_buttons',
  id    = 'type',
  label = "Do you want to register publication metadata, or an indicator  presented within an already registered publication?",
  option = c(
    'Publication'    = 'pub',
    'Indicator' = 'ind'
  )
)
```

```{r}
sd_next()
```
:::

::: {#pubPage .sd-page}
## Register a publication

Before processing individual indicators, you first need to register meta data about the publication. Later you will link the indicator registration form to this publication record.

```{r q-thirdpage}
sd_question(
  type  = 'numeric',
  id    = 'age',
  label = "What's your age?"
)



sd_next(next_page = 'end')

```
:::

::: {#indPage .sd-page}
Register an indicator

Link the indicator to a publication by first finding the publication in the datatable below, and copying the session_id into the text field.

<!--# This is suboptimal, but updateSelectInput did nt work, nor did adding slectInput (or pickerInput) as UI object from the server. If I did that, the picker input did not register as a question on suprabase. -->

```{r q-link}
sd_question(
  type = "text",
  id = 'select_pub4',
  label = "Paste publication ID"
)

uiOutput('mydata_X')
```

```{r}
sd_next(next_page = 'end')
```
:::

::: {#end .sd-page}
## End

This it the last page in the survey.

```{r}
sd_close("Exit Survey")
```
:::
